Network Data Collection for Artifical Intelligence

### 2020-02-25 paper2/paper2.tex

There also exists a large number of techniques for dimensionality reduction. The 40 features of the NSL-KDD data set could be reduced to 30 or 16 features, with no or low degradation in detection power. The benefits of a reduced feature set are faster processing, less memory consumption, and in some cases even higher detection precision, because some classifiers have problems with irrelevant or correlated features. This could be achieved by combining the following methods \cite{vasquez2014}:
\begin{itemize}
	\item Weight by maximum relevance
	\item Minimum redundancy maximum relevance
	\item Significance analysis for microarrays
	\item Least absolute selection and shrinkage operator
	\item Stability selection
	\item Stepwise regression
\end{itemize}

@@

\bibitem{vasquez2014} Vázquez, F. Iglesias and Zseby, T. (2014). Analysis of network traffic features for anomaly detection. Machine Learning, vol. 101, 12 2014.

@@

\bibitem{dehghani2010} Dehghani, F. and Movahhedinia, N. and Khayyambashi, M. R. and Kianian, S. (2010). Real-time Traffic Classification Based on Statistical and Payload Content Features. 2010 2nd International Workshop on Intelligent Systems and Applications, Wuhan, pp. 1-4, 2010.

@@

\bibitem{sopuru2019} Sopuru, J. and Sari, A. and Akkaya, M. (2019). Modeling A Malware Detection And Categorization System Based On Seven Network Flow-Based Features. International Journal of Innovative Technology and Exploring Engineering (IJITEE), vol. 8(7), pp. 2982-2989, 05 2019

@@

\bibitem{mantere2013} Mantere, M. and Sailio, M. and Noponen, S. (2013). Network Traffic Features for Anomaly Detection in Specific Industrial Control System Network. Future Internet, vol. 5, pp. 460-473, 2013
\bibitem{brownlee1998} Brownlee, N. (1998). Network management and realtime traffic flowmeasurement. J. Netw. Syst. Manage., vol. 6, p. 223–228, June 1998.
\bibitem{waizumi2007} Waizumi, Y. and Sato, Y. and Nemoto, Y. (2007). A network-based anomaly detection system using multiple network features. WEBIST, 2007.

@@

\bibitem{lashkari2017} Lashkari, A. H. and Gil, G. D. and Mamun, M. S. I. and Ghorbani, A. A. (2017). Characterization of Tor Traffic using Time based Features. Proceedings of the 3rd International Conference on Information Systems Security and Privacy (ICISSP 2017), pp. 253-262, 2017.
\bibitem{wang2018} Wang, W. and Sheng, Y. and Wang, J. and and Zeng, X. and Ye, X. and Huang, Y. and Zhu, M. (2018). HAST-IDS: Learning Hierarchical Spatial-Temporal Features Using Deep Neural Networks to Improve Intrusion Detection. IEEE Access, vol. 6, pp. 1792-1806, 2018.
\bibitem{yen2011} Yen, T. (2011). Detecting stealthy malware using behavioralfeatures in network traffic. PhD thesis, Carnegie Mellon University, 2011.

>>>>

There also exists a large number of techniques for dimensionality reduction. The 40 features of the NSL-KDD data set could be reduced to 30 or 16 features, with no or low degradation in detection power. The benefits of a reduced feature set are faster processing, less memory consumption, and in some cases even higher detection precision, because some classifiers have problems with irrelevant or correlated features. This could be achieved by combining the following methods \cite{vasquez2015}:
\begin{itemize}
	\item Weight by maximum relevance
	\item Minimum redundancy maximum relevance
	\item Significance analysis for microarrays
	\item Least absolute selection and shrinkage operator
	\item Stability selection
	\item Stepwise regression
\end{itemize}

@@

\bibitem{vasquez2015} Vázquez Iglesias, F. and Zseby, T. (2015). Analysis of network traffic features for anomaly detection. Machine Learning, vol. 101, 2015.

@@

\bibitem{dehghani2010} Dehghani, F. and Movahhedinia, N. and Khayyambashi, M. R. and Kianian, S. (2010). Real-time traffic classification based on statistical and payload content features. 2010 2nd International Workshop on Intelligent Systems and Applications, Wuhan, pp. 1-4, 2010.

@@

\bibitem{sopuru2019} Sopuru, J. and Sari, A. and Akkaya, M. (2019). Modeling a malware detection and categorization system based on seven network flow-based features. International Journal of Innovative Technology and Exploring Engineering (IJITEE), vol. 8(7), pp. 2982-2989, 05 2019

@@

\bibitem{mantere2013} Mantere, M. and Sailio, M. and Noponen, S. (2013). Network traffic features for anomaly detection in specific industrial control system network. Future Internet, vol. 5, pp. 460-473, 2013
\bibitem{brownlee1998} Brownlee, N. (1998). Network management and realtime traffic flowmeasurement. J. Netw. Syst. Manage., vol. 6, pp. 223–228, June 1998.
\bibitem{waizumi2007} Waizumi, Y. and Sato, Y. and Nemoto, Y. (2007). A network-based anomaly detection system using multiple network features. Proceedings of the Third International Conference on Web Information Systems and Technologies - Internet Technology, pp. 410-413, 2007.

@@

\bibitem{lashkari2017} Lashkari, A. H. and Gil, G. D. and Mamun, M. S. I. and Ghorbani, A. A. (2017). Characterization of tor traffic using time based features. Proceedings of the 3rd International Conference on Information Systems Security and Privacy (ICISSP 2017), pp. 253-262, 2017.
\bibitem{wang2018} Wang, W. and Sheng, Y. and Wang, J. and and Zeng, X. and Ye, X. and Huang, Y. and Zhu, M. (2018). HAST-IDS: Learning hierarchical spatial-temporal features Using deep neural networks to improve intrusion detection. IEEE Access, vol. 6, pp. 1792-1806, 2018.
\bibitem{yen2011} Yen, T. (2011). Detecting stealthy malware using behavioral features in network traffic. PhD thesis, Carnegie Mellon University, 2011.
